Safe and Robust Formal Synthesis of Digital Controllers\\ for Continuous Plants

### 2018-03-20 automatica/paper.tex
comment on termination
naive back end handles fixed or float

The design consists of two phases, an inductive synthesis phase (denoted by {\sc Synthesize} in
Figure~\ref{fig:CEGIS}) and a validation phase (denoted by {\sc
  Verify}), which interact via a finite set of tests {\sc
  inputs} that is updated incrementally.  Given the specification $\phi$, the inductive synthesis procedure tries to
find an existential witness $P$ satisfying the specification
$\phi(a, P)$ for all $a$ in {\sc inputs} (as opposed to all $a \in
\mathcal{D}$).
%
If the synthesis phase succeeds in finding a witness~$P$, this witness is a
candidate solution to the full synthesis formula.  We pass this candidate
solution to the validation phase, which checks whether it is a full solution
(i.e., $P$ satisfies the specification $\phi(a, P)$ for all
$a\in\mathcal{D}$).  If this is the case, then the algorithm terminates. 
Otherwise, additional information is provided to the inductive synthesis
phase in the form of a new counterexample that is added to the {\sc inputs}
set and the loop iterates again.  %% More details about the general
%% architecture of the synthesizer can be found
%% in~\cite{DBLP:conf/lpar/DavidKL15}.
[COMMENT ON TERMINATION?]

%-------------------------------
\section{Formal specification of model properties} 
\label{sec:specification}
%-------------------------------

@@

Regarding the second requirement, we synthesize a safe controller by
unfolding the transition system $k$ steps and by picking a controller $K$
and a single initial state, such that the states at each step do not violate
the safety criteria.  That is, we ask the bounded model checker if there
exists a $K$ that is safe for at least one $x_0$ in our set of all possible
initial states.  This is sound if the current $k$ is greater than the completeness
threshold.  We~also assume some precision $\langle I_p,F_p\rangle$ for the
plant and a sampling rate.  The checks that these assumptions hold are
performed by subsequent {\sc verify} stages.

>>>>

The design consists of two phases, an inductive synthesis phase (denoted by {\sc Synthesize} in
Figure~\ref{fig:CEGIS}) and a validation phase (denoted by {\sc
  Verify}), which interact via a finite set of tests {\sc
  inputs} that is updated incrementally.  Given the specification $\phi$, the inductive synthesis procedure tries to
find an existential witness $P$ satisfying the specification
$\phi(a, P)$ for all $a$ in {\sc inputs} (as opposed to all $a \in
\mathcal{D}$).
%
If the synthesis phase succeeds in finding a witness~$P$, this witness is a
candidate solution to the full synthesis formula.  We pass this candidate
solution to the validation phase, which checks whether it is a full solution
(i.e., $P$ satisfies the specification $\phi(a, P)$ for all
$a\in\mathcal{D}$).  If this is the case, then the algorithm terminates. 
Otherwise, additional information is provided to the inductive synthesis
phase in the form of a new counterexample that is added to the {\sc inputs}
set and the loop iterates again.  %% More details about the general
%% architecture of the synthesizer can be found
%% in~\cite{DBLP:conf/lpar/DavidKL15}.
[COMMENT ON TERMINATION?]
CEGIS in general is not guaranteed to terminate if the search space is infinite. 
%-------------------------------
\section{Formal specification of model properties} 
\label{sec:specification}
%-------------------------------

@@

Regarding the second requirement, we synthesize a safe controller by
unfolding the transition system $k$ steps and by picking a controller $K$
and a single initial state, such that the states at each step do not violate
the safety criteria.  That is, we ask the bounded model checker if there
exists a $K$ that is safe for at least one $x_0$ in our set of all possible
initial states.  This is sound if the current $k$ is greater than the completeness
threshold.  We~also assume some (fixed or floating point) precision $\langle I_p,F_p\rangle$ for the
plant and a sampling rate.  The checks that these assumptions hold are
performed by subsequent {\sc verify} stages.
